---
title: "File Format Statistics"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(readr)
library(stringdist)
library(PairedData)
```


Bit(2)-Bit(5)
```{r echo=FALSE}
BetweenSymptomsStats <- read_delim("D:/ExperimentLogs/BetweenSymptomsStats_2Vs5.txt", ";", escape_double = FALSE, trim_ws = TRUE, col_types = cols(
  .default = col_double(),
  Project = col_character(),
  PrincipalRevisionPair = col_character()
))

total <- nrow(BetweenSymptomsStats)
sprintf("TOTAL %g", total)
sprintf("LR: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),])/total*100, 2))
sprintf("RL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),])/total*100, 2))
sprintf("LRorRL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),])/total*100, 2))
sprintf("L_leq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("R_leq_L: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("L_neq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),])/total*100, 2))

summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[1]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[3]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[6]

res <- wilcox.test(as.vector(BetweenSymptomsStats$`#actions_2Vs5`), 
                   as.vector(BetweenSymptomsStats$`#actions_5Vs2`), 
                   paired = TRUE,
                   alternative = "less")
res
```

Cit(32)-Cit(33)
```{r echo=FALSE}
BetweenSymptomsStats <- read_delim("D:/ExperimentLogs/BetweenSymptomsStats_32Vs33.txt", ";", escape_double = FALSE, trim_ws = TRUE, col_types = cols(
  .default = col_double(),
  Project = col_character(),
  PrincipalRevisionPair = col_character()
))

total <- nrow(BetweenSymptomsStats)
sprintf("TOTAL %g", total)
sprintf("LR: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),])/total*100, 2))
sprintf("RL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),])/total*100, 2))
sprintf("LRorRL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),])/total*100, 2))
sprintf("L_leq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("R_leq_L: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("L_neq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),])/total*100, 2))

summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[1]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[3]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[6]

res <- wilcox.test(as.vector(BetweenSymptomsStats$`#actions_32Vs33`), 
                   as.vector(BetweenSymptomsStats$`#actions_33Vs32`), 
                   paired = TRUE,
                   alternative = "greater")
res
```

Cet(10)-Cet(11)
```{r echo=FALSE}
BetweenSymptomsStats <- read_delim("D:/ExperimentLogs/BetweenSymptomsStats_10Vs11.txt", ";", escape_double = FALSE, trim_ws = TRUE, col_types = cols(
  .default = col_double(),
  Project = col_character(),
  PrincipalRevisionPair = col_character()
))

total <- nrow(BetweenSymptomsStats)
sprintf("TOTAL %g", total)
sprintf("LR: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),])/total*100, 2))
sprintf("RL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),])/total*100, 2))
sprintf("LRorRL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),])/total*100, 2))
sprintf("L_leq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("R_leq_L: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("L_neq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),])/total*100, 2))

summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[1]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[3]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[6]

res <- wilcox.test(as.vector(BetweenSymptomsStats$`#actions_10Vs11`), 
                   as.vector(BetweenSymptomsStats$`#actions_11Vs10`), 
                   paired = TRUE,
                   alternative = "greater")
res
```

Dit(30)-Dit(31)
```{r echo=FALSE}
BetweenSymptomsStats <- read_delim("D:/ExperimentLogs/BetweenSymptomsStats_30Vs31.txt", ";", escape_double = FALSE, trim_ws = TRUE, col_types = cols(
  .default = col_double(),
  Project = col_character(),
  PrincipalRevisionPair = col_character()
))

total <- nrow(BetweenSymptomsStats)
sprintf("TOTAL %g", total)
sprintf("LR: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),])/total*100, 2))
sprintf("RL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),])/total*100, 2))
sprintf("LRorRL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),])/total*100, 2))
sprintf("L_leq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("R_leq_L: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("L_neq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),])/total*100, 2))

summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[1]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[3]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[6]

res <- wilcox.test(as.vector(BetweenSymptomsStats$`#actions_30Vs31`), 
                   as.vector(BetweenSymptomsStats$`#actions_31Vs30`), 
                   paired = TRUE,
                   alternative = "greater")
res
```
Det(28)-Det(29)
```{r echo=FALSE}
BetweenSymptomsStats <- read_delim("D:/ExperimentLogs/BetweenSymptomsStats_28Vs29.txt", ";", escape_double = FALSE, trim_ws = TRUE, col_types = cols(
  .default = col_double(),
  Project = col_character(),
  PrincipalRevisionPair = col_character()
))

total <- nrow(BetweenSymptomsStats)
sprintf("TOTAL %g", total)
sprintf("LR: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),])/total*100, 2))
sprintf("RL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),])/total*100, 2))
sprintf("LRorRL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),])/total*100, 2))
sprintf("L_leq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("R_leq_L: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("L_neq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),])/total*100, 2))

summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[1]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[3]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[6]

res <- wilcox.test(as.vector(BetweenSymptomsStats$`#actions_28Vs29`), 
                   as.vector(BetweenSymptomsStats$`#actions_29Vs28`), 
                   paired = TRUE,
                   alternative = "greater")
res
```

Eit(36)-Eit(37)
```{r echo=FALSE}
BetweenSymptomsStats <- read_delim("D:/ExperimentLogs/BetweenSymptomsStats_36Vs37.txt", ";", escape_double = FALSE, trim_ws = TRUE, col_types = cols(
  .default = col_double(),
  Project = col_character(),
  PrincipalRevisionPair = col_character()
))

total <- nrow(BetweenSymptomsStats)
sprintf("TOTAL %g", total)
sprintf("LR: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),])/total*100, 2))
sprintf("RL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),])/total*100, 2))
sprintf("LRorRL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),])/total*100, 2))
sprintf("L_leq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("R_leq_L: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("L_neq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),])/total*100, 2))

summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[1]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[3]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[6]

res <- wilcox.test(as.vector(BetweenSymptomsStats$`#actions_36Vs37`), 
                   as.vector(BetweenSymptomsStats$`#actions_37Vs36`), 
                   paired = TRUE,
                   alternative = "greater")
res
```

Eet(34)-Eet(35)
```{r echo=FALSE}
BetweenSymptomsStats <- read_delim("D:/ExperimentLogs/BetweenSymptomsStats_34Vs35.txt", ";", escape_double = FALSE, trim_ws = TRUE, col_types = cols(
  .default = col_double(),
  Project = col_character(),
  PrincipalRevisionPair = col_character()
))

total <- nrow(BetweenSymptomsStats)
sprintf("TOTAL %g", total)
sprintf("LR: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),])/total*100, 2))
sprintf("RL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),])/total*100, 2))
sprintf("LRorRL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),])/total*100, 2))
sprintf("L_leq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("R_leq_L: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("L_neq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),])/total*100, 2))

summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[1]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[3]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[6]

res <- wilcox.test(as.vector(BetweenSymptomsStats$`#actions_34Vs35`), 
                   as.vector(BetweenSymptomsStats$`#actions_35Vs34`), 
                   paired = TRUE,
                   alternative = "greater")
res
```

Cet(10)-Cit(32)
```{r echo=FALSE}
BetweenSymptomsStats <- read_delim("D:/ExperimentLogs/BetweenSymptomsStats_10Vs32.txt", ";", escape_double = FALSE, trim_ws = TRUE, col_types = cols(
  .default = col_double(),
  Project = col_character(),
  PrincipalRevisionPair = col_character()
))

total <- nrow(BetweenSymptomsStats)
sprintf("TOTAL %g", total)
sprintf("LR: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),])/total*100, 2))
sprintf("RL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),])/total*100, 2))
sprintf("LRorRL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),])/total*100, 2))
sprintf("L_leq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("R_leq_L: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("L_neq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),])/total*100, 2))

summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[1]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[3]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[6]

res <- wilcox.test(as.vector(BetweenSymptomsStats$`#actions_10Vs32`), 
                   as.vector(BetweenSymptomsStats$`#actions_32Vs10`), 
                   paired = TRUE,
                   alternative = "greater")
res
```

Det(28)-Dit(30)
```{r echo=FALSE}
BetweenSymptomsStats <- read_delim("D:/ExperimentLogs/BetweenSymptomsStats_28Vs30.txt", ";", escape_double = FALSE, trim_ws = TRUE, col_types = cols(
  .default = col_double(),
  Project = col_character(),
  PrincipalRevisionPair = col_character()
))

total <- nrow(BetweenSymptomsStats)
sprintf("TOTAL %g", total)
sprintf("LR: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),])/total*100, 2))
sprintf("RL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),])/total*100, 2))
sprintf("LRorRL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),])/total*100, 2))
sprintf("L_leq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("R_leq_L: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("L_neq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),])/total*100, 2))

summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[1]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[3]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[6]

res <- wilcox.test(as.vector(BetweenSymptomsStats$`#actions_28Vs30`), 
                   as.vector(BetweenSymptomsStats$`#actions_30Vs28`), 
                   paired = TRUE,
                   alternative = "less")
res
```

Eet(34)-Eit(36)
```{r echo=FALSE}
BetweenSymptomsStats <- read_delim("D:/ExperimentLogs/BetweenSymptomsStats_34Vs36.txt", ";", escape_double = FALSE, trim_ws = TRUE, col_types = cols(
  .default = col_double(),
  Project = col_character(),
  PrincipalRevisionPair = col_character()
))

total <- nrow(BetweenSymptomsStats)
sprintf("TOTAL %g", total)
sprintf("LR: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),])/total*100, 2))
sprintf("RL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),])/total*100, 2))
sprintf("LRorRL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),])/total*100, 2))
sprintf("L_leq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("R_leq_L: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("L_neq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),])/total*100, 2))

summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[1]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[3]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[6]

res <- wilcox.test(as.vector(BetweenSymptomsStats$`#actions_34Vs36`), 
                   as.vector(BetweenSymptomsStats$`#actions_36Vs34`), 
                   paired = TRUE,
                   alternative = "less")
res
```

Cet(10)-Det(28)
```{r echo=FALSE}
BetweenSymptomsStats <- read_delim("D:/ExperimentLogs/BetweenSymptomsStats_10Vs28.txt", ";", escape_double = FALSE, trim_ws = TRUE, col_types = cols(
  .default = col_double(),
  Project = col_character(),
  PrincipalRevisionPair = col_character()
))

total <- nrow(BetweenSymptomsStats)
sprintf("TOTAL %g", total)
sprintf("LR: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),])/total*100, 2))
sprintf("RL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),])/total*100, 2))
sprintf("LRorRL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),])/total*100, 2))
sprintf("L_leq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("R_leq_L: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("L_neq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),])/total*100, 2))

summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[1]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[3]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[6]

res <- wilcox.test(as.vector(BetweenSymptomsStats$`#actions_10Vs28`), 
                   as.vector(BetweenSymptomsStats$`#actions_28Vs10`), 
                   paired = TRUE,
                   alternative = "greater")
res
```

Cet(10)-Dit(30)
```{r echo=FALSE}
BetweenSymptomsStats <- read_delim("D:/ExperimentLogs/BetweenSymptomsStats_10Vs30.txt", ";", escape_double = FALSE, trim_ws = TRUE, col_types = cols(
  .default = col_double(),
  Project = col_character(),
  PrincipalRevisionPair = col_character()
))

total <- nrow(BetweenSymptomsStats)
sprintf("TOTAL %g", total)
sprintf("LR: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),])/total*100, 2))
sprintf("RL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),])/total*100, 2))
sprintf("LRorRL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),])/total*100, 2))
sprintf("L_leq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("R_leq_L: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("L_neq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),])/total*100, 2))

summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[1]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[3]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[6]

res <- wilcox.test(as.vector(BetweenSymptomsStats$`#actions_10Vs30`), 
                   as.vector(BetweenSymptomsStats$`#actions_30Vs10`), 
                   paired = TRUE,
                   alternative = "greater")
res
```

Cit(32)-Det(28)
```{r echo=FALSE}
BetweenSymptomsStats <- read_delim("D:/ExperimentLogs/BetweenSymptomsStats_28Vs32.txt", ";", escape_double = FALSE, trim_ws = TRUE, col_types = cols(
  .default = col_double(),
  Project = col_character(),
  PrincipalRevisionPair = col_character()
))

total <- nrow(BetweenSymptomsStats)
sprintf("TOTAL %g", total)
sprintf("LR: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),])/total*100, 2))
sprintf("RL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),])/total*100, 2))
sprintf("LRorRL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),])/total*100, 2))
sprintf("L_leq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("R_leq_L: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("L_neq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),])/total*100, 2))

summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[1]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[3]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[6]

res <- wilcox.test(as.vector(BetweenSymptomsStats$`#actions_28Vs32`), 
                   as.vector(BetweenSymptomsStats$`#actions_32Vs28`), 
                   paired = TRUE,
                   alternative = "less")
res
```

Cit(32)-Dit(30)
```{r echo=FALSE}
BetweenSymptomsStats <- read_delim("D:/ExperimentLogs/BetweenSymptomsStats_30Vs32.txt", ";", escape_double = FALSE, trim_ws = TRUE, col_types = cols(
  .default = col_double(),
  Project = col_character(),
  PrincipalRevisionPair = col_character()
))

total <- nrow(BetweenSymptomsStats)
sprintf("TOTAL %g", total)
sprintf("LR: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),])/total*100, 2))
sprintf("RL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),])/total*100, 2))
sprintf("LRorRL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),])/total*100, 2))
sprintf("L_leq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("R_leq_L: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("L_neq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),])/total*100, 2))

summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[1]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[3]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[6]

res <- wilcox.test(as.vector(BetweenSymptomsStats$`#actions_30Vs32`), 
                   as.vector(BetweenSymptomsStats$`#actions_32Vs30`), 
                   paired = TRUE,
                   alternative = "less")
res
```

Cet(10)-Eet(34)
```{r echo=FALSE}
BetweenSymptomsStats <- read_delim("D:/ExperimentLogs/BetweenSymptomsStats_10Vs34.txt", ";", escape_double = FALSE, trim_ws = TRUE, col_types = cols(
  .default = col_double(),
  Project = col_character(),
  PrincipalRevisionPair = col_character()
))

total <- nrow(BetweenSymptomsStats)
sprintf("TOTAL %g", total)
sprintf("LR: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),])/total*100, 2))
sprintf("RL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),])/total*100, 2))
sprintf("LRorRL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),])/total*100, 2))
sprintf("L_leq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("R_leq_L: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("L_neq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),])/total*100, 2))

summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[1]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[3]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[6]

res <- wilcox.test(as.vector(BetweenSymptomsStats$`#actions_10Vs34`), 
                   as.vector(BetweenSymptomsStats$`#actions_34Vs10`), 
                   paired = TRUE,
                   alternative = "less")
res
```

Cet(10)-Eit(36)
```{r echo=FALSE}
BetweenSymptomsStats <- read_delim("D:/ExperimentLogs/BetweenSymptomsStats_10Vs36.txt", ";", escape_double = FALSE, trim_ws = TRUE, col_types = cols(
  .default = col_double(),
  Project = col_character(),
  PrincipalRevisionPair = col_character()
))

total <- nrow(BetweenSymptomsStats)
sprintf("TOTAL %g", total)
sprintf("LR: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),])/total*100, 2))
sprintf("RL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),])/total*100, 2))
sprintf("LRorRL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),])/total*100, 2))
sprintf("L_leq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("R_leq_L: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("L_neq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),])/total*100, 2))

summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[1]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[3]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[6]

res <- wilcox.test(as.vector(BetweenSymptomsStats$`#actions_10Vs36`), 
                   as.vector(BetweenSymptomsStats$`#actions_36Vs10`), 
                   paired = TRUE,
                   alternative = "less")
res
```

Cit(32)-Eet(34)
```{r echo=FALSE}
BetweenSymptomsStats <- read_delim("D:/ExperimentLogs/BetweenSymptomsStats_32Vs34.txt", ";", escape_double = FALSE, trim_ws = TRUE, col_types = cols(
  .default = col_double(),
  Project = col_character(),
  PrincipalRevisionPair = col_character()
))

total <- nrow(BetweenSymptomsStats)
sprintf("TOTAL %g", total)
sprintf("LR: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[28] != 0),])/total*100, 2))
sprintf("RL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[29] != 0),])/total*100, 2))
sprintf("LRorRL: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),])/total*100, 2))
sprintf("L_leq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] < BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("R_leq_L: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] > BetweenSymptomsStats[22]),])/total*100, 2))
sprintf("L_neq_R: %g (%g%%)", nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),]), round(nrow(BetweenSymptomsStats[which(BetweenSymptomsStats[16] != BetweenSymptomsStats[22]),])/total*100, 2))

summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[1]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[3]
summary(BetweenSymptomsStats[which(BetweenSymptomsStats[27] != 0),][27])[6]

res <- wilcox.test(as.vector(BetweenSymptomsStats$`#actions_32Vs34`), 
                   as.vector(BetweenSymptomsStats$`#actions_34Vs32`), 
                   paired = TRUE,
                   alternative = "less")
res
```

```{r cars, echo=FALSE}
library(readr)
fileformat_stats_1_5_12_20_28_44_60 <- read_delim("D:/ExperimentLogs/fileformat-stats_1_5_12_20_28_44_60.txt", 
    ";", escape_double = FALSE, trim_ws = TRUE)
stats <- fileformat_stats_1_5_12_20_28_44_60[which(
  fileformat_stats_1_5_12_20_28_44_60$`1` != -1 & 
  fileformat_stats_1_5_12_20_28_44_60$`5` != -1 & 
  fileformat_stats_1_5_12_20_28_44_60$`12` != -1 & 
  fileformat_stats_1_5_12_20_28_44_60$`20` != -1 & 
  fileformat_stats_1_5_12_20_28_44_60$`28` != -1 & 
  fileformat_stats_1_5_12_20_28_44_60$`44` != -1 & 
  fileformat_stats_1_5_12_20_28_44_60$`60` != -1),]

nrow(stats)
```

## Including Plots

File format (1) - srcML:
```{r kind1, echo=FALSE}
srcmlStats <- summary(stats[which(stats$`1` != -1),]$`1`)
srcmlStats
```
File format (20) - RoslynML (IncludeTrivia):
```{r kind20, echo=FALSE}
fullRoslynmlStats <- summary(stats[which(stats$`20` != -1),]$`20`)
fullRoslynmlStats
sprintf("Percentage regarding srcML: %g", ((srcmlStats[4] - fullRoslynmlStats[4])/max(srcmlStats[4], fullRoslynmlStats[4]) * 100))
```

File format (5) - RoslynML:
```{r kind5, echo=FALSE}
stats1 <- summary(stats[which(stats$`5` != -1),]$`5`)
stats1
sprintf("Percentage regarding srcML: %g", ((srcmlStats[4] - stats1[4])/max(srcmlStats[4], stats1[4]) * 100))
sprintf("Percentage regarding RoslynML+trivia: %g", ((fullRoslynmlStats[4] - stats1[4])/max(stats1[4], fullRoslynmlStats[4]) * 100))
```


File format (12) - RoslynML (BasicPruning):
```{r kind12, echo=FALSE}
summary(stats[which(stats$`12` != -1),]$`12`)
```

File format (28) - RoslynML (IncludeTrivia BasicPruning):
```{r kind28, echo=FALSE}
stats1 <- summary(stats[which(stats$`28` != -1),]$`28`)
stats1
sprintf("Percentage regarding srcML: %g", ((srcmlStats[4] - stats1[4])/max(srcmlStats[4], stats1[4]) * 100))
sprintf("Percentage regarding RoslynML+trivia: %g", ((fullRoslynmlStats[4] - stats1[4])/max(stats1[4], fullRoslynmlStats[4]) * 100))
```

File format (44) - RoslynML (BasicPruning Defoliation):
```{r kind44, echo=FALSE}
stats1 <- summary(stats[which(stats$`44` != -1),]$`44`)
stats1
sprintf("Percentage regarding srcML: %g", ((srcmlStats[4] - stats1[4])/max(srcmlStats[4], stats1[4]) * 100))
sprintf("Percentage regarding RoslynML+trivia: %g", ((fullRoslynmlStats[4] - stats1[4])/max(stats1[4], fullRoslynmlStats[4]) * 100))
```

File format (60) - RoslynML (IncludeTrivia BasicPruning Defoliation):
```{r kind60, echo=FALSE}
stats1 <- summary(stats[which(stats$`60` != -1),]$`60`)
stats1
sprintf("Percentage regarding srcML: %g", ((srcmlStats[4] - stats1[4])/max(srcmlStats[4], stats1[4]) * 100))
sprintf("Percentage regarding RoslynML+trivia: %g", ((fullRoslynmlStats[4] - stats1[4])/max(stats1[4], fullRoslynmlStats[4]) * 100))
```